Equations & R Code

### 2017-03-31 manuscript/coexistence-stability_ms.Rmd
trivial updates to text

@@

\new{We limit our analysis to four species communities because it is exceedingly difficult to get more than four species to coexist via relative nonlinearity without introducing some form of fluctuation-independent mechanism like resource partitioning} [@Yuan2015], \new{which would then cloud our inference on the effect of fluctuation-dependent coexistence.
For consistency, we also constrain our focus to four species communities under the storage effect, but our conclusions apply to more species-rich communities (see Supporting Information section SI.2).}

@@

The dampening effect of fluctuation-dependent coexistence on increasing environmental variability depends on the specific traits (parameter values) of the species in the regional pool.
\new{Under the storage effect, moderately asymmetric competition} makes it more difficult for new species to enter the local community, but once they do enter, ecosystem *CV* is similar between communities with low and moderate competitive asymmetries (Fig. 3; compare top and bottom panels).
Moderately asymmetric competition does decrease the rate at which ecosystem *CV* increases with environmental variance (Fig. SI-8) because the abundance of inferior competitors is reduced and they do not influence ecosystem *CV* as much as when competitive asymmetry is low.
The correlation of species' environmental responses ($\rho$) also mediates the relationship between environmental variance, species richness, and ecosystem *CV*: lower correlations make it easier for new species to enter the community and contribute to porfolio effects (Fig. 3).
When the correlation of species' environmental responses were as negative as possible ($\rho = -1/3$), ecosystem *CV* of the four-species community was immune to increases in the environmental cue variance (Fig. 3A).
However, more extreme increases in the variance of the environmental cue, which increase the number of extremely low or high germination events (i.e., $\gamma \approx 0$ or 1$; Fig. SI-9), eventually caused ecosystem *CV* to increase in the four species community (Fig. SI-10).

>>>>

\new{We limit our analysis to four-species communities because it is exceedingly difficult to get more than four species to coexist via relative nonlinearity without introducing some form of fluctuation-independent mechanism like resource partitioning} [@Yuan2015], \new{which would then cloud our inference on the effect of fluctuation-dependent coexistence.
For consistency, we also constrain our focus to four species communities under the storage effect, but our conclusions apply to more species-rich communities (see Supporting Information section SI.2).}

@@

@@

The dampening effect of fluctuation-dependent coexistence on increasing environmental variability depends on the specific traits (parameter values) of the species in the regional pool.
\new{Under the storage effect, moderately asymmetric competition} makes it more difficult for new species to enter the local community, but once they do enter, ecosystem *CV* is similar between communities with low and moderate competitive asymmetries (Fig. 3; compare top and bottom panels).
Moderately asymmetric competition does decrease the rate at which ecosystem *CV* increases with environmental variance (Fig. SI-8) because the abundance of inferior competitors is reduced and they do not influence ecosystem *CV* as much as when competitive asymmetry is low.
The correlation of species' environmental responses ($\rho$) also mediates the relationship between environmental variance, species richness, and ecosystem *CV*: lower correlations make it easier for new species to enter the community and contribute to porfolio effects (Fig. 3).
When the correlation of species' environmental responses were as negative as possible ($\rho = -1/3$), ecosystem *CV* of the four-species community was immune to increases in the environmental cue variance (Fig. 3A).
However, more extreme increases in the variance of the environmental cue, which increase the number of extremely low or high germination events (i.e., $\gamma \approx 0$ or 1; Fig. SI-9), eventually caused ecosystem *CV* to increase in the four species community (Fig. SI-10).

### 2017-03-31 manuscript/coexistence-stability_ms.tex
trivial updates to text

@@

\new{We limit our analysis to four species communities because it is exceedingly difficult to get more than four species to coexist via relative nonlinearity without introducing some form of fluctuation-independent mechanism like resource partitioning}
(Yuan \& Chesson 2015),
\new{which would then cloud our inference on the effect of fluctuation-dependent coexistence.
For consistency, we also constrain our focus to four species communities under the storage effect, but our conclusions apply to more species-rich communities (see Supporting Information section SI.2).}

@@

The dampening effect of fluctuation-dependent coexistence on increasing
environmental variability depends on the specific traits (parameter
values) of the species in the regional pool.
\new{Under the storage effect, moderately asymmetric competition} makes
it more difficult for new species to enter the local community, but once
they do enter, ecosystem \emph{CV} is similar between communities with
low and moderate competitive asymmetries (Fig. 3; compare top and bottom
panels). Moderately asymmetric competition does decrease the rate at
which ecosystem \emph{CV} increases with environmental variance (Fig.
SI-8) because the abundance of inferior competitors is reduced and they
do not influence ecosystem \emph{CV} as much as when competitive
asymmetry is low. The correlation of species' environmental responses
(\(\rho\)) also mediates the relationship between environmental
variance, species richness, and ecosystem \emph{CV}: lower correlations
make it easier for new species to enter the community and contribute to
porfolio effects (Fig. 3). When the correlation of species'
environmental responses were as negative as possible (\(\rho = -1/3\)),
ecosystem \emph{CV} of the four-species community was immune to
increases in the environmental cue variance (Fig. 3A). However, more
extreme increases in the variance of the environmental cue, which
increase the number of extremely low or high germination events (i.e.,
\(\gamma \approx 0\) or 1\$; Fig. SI-9), eventually caused ecosystem
\emph{CV} to increase in the four species community (Fig. SI-10).

>>>>

\new{We limit our analysis to four-species communities because it is exceedingly difficult to get more than four species to coexist via relative nonlinearity without introducing some form of fluctuation-independent mechanism like resource partitioning}
(Yuan \& Chesson 2015),
\new{which would then cloud our inference on the effect of fluctuation-dependent coexistence.
For consistency, we also constrain our focus to four species communities under the storage effect, but our conclusions apply to more species-rich communities (see Supporting Information section SI.2).}

@@

@@

The dampening effect of fluctuation-dependent coexistence on increasing
environmental variability depends on the specific traits (parameter
values) of the species in the regional pool.
\new{Under the storage effect, moderately asymmetric competition} makes
it more difficult for new species to enter the local community, but once
they do enter, ecosystem \emph{CV} is similar between communities with
low and moderate competitive asymmetries (Fig. 3; compare top and bottom
panels). Moderately asymmetric competition does decrease the rate at
which ecosystem \emph{CV} increases with environmental variance (Fig.
SI-8) because the abundance of inferior competitors is reduced and they
do not influence ecosystem \emph{CV} as much as when competitive
asymmetry is low. The correlation of species' environmental responses
(\(\rho\)) also mediates the relationship between environmental
variance, species richness, and ecosystem \emph{CV}: lower correlations
make it easier for new species to enter the community and contribute to
porfolio effects (Fig. 3). When the correlation of species'
environmental responses were as negative as possible (\(\rho = -1/3\)),
ecosystem \emph{CV} of the four-species community was immune to
increases in the environmental cue variance (Fig. 3A). However, more
extreme increases in the variance of the environmental cue, which
increase the number of extremely low or high germination events (i.e.,
\(\gamma \approx 0\) or 1; Fig. SI-9), eventually caused ecosystem
\emph{CV} to increase in the four species community (Fig. SI-10).
